### Background
```{r}
library(tidyverse)
```

### Data
Load stream chemistry data from downloaded csv files.
```{r}
bisley1 <- read_csv("data/bisley1.csv")
bisley2 <- read_csv("data/bisley2.csv")
bisley3 <- read_csv("data/bisley3.csv")
prm <- read_csv("data/prm.csv")
```

### Methods
Call the "moving average" function so that we can create moving window averages for the stream chemistry data.
```{r}
source("R/moving-average.R")
```

Clean the data files by selecting only the relevant columns and adding a "site" column to keep track of sites once the data files are merged.
```{r}
cleaned_bis_1 <- bisley1 |> 
  select(`NH4-N`, `NO3-N`, Sample_Date, K, Ca, Mg) |> 
  mutate(Site = "BQ1")
cleaned_bis_2 <- bisley2 |> 
  select(`NH4-N`, `NO3-N`, Sample_Date, K, Ca, Mg) |> 
  mutate(Site = "BQ2")
cleaned_bis_3 <- bisley3 |> 
  select(`NH4-N`, `NO3-N`, Sample_Date, K, Ca, Mg) |> 
  mutate(Site = "BQ3")
cleaned_prm <- prm |> 
  select(`NH4-N`, `NO3-N`, Sample_Date, K, Ca, Mg) |> 
  mutate(Site = "PRM")
```


Call the "moving_average" function on each dataset.
```{r}
bq1_window <- moving_average(cleaned_bis_1)
bq2_window <- moving_average(cleaned_bis_2)
bq3_window <- moving_average(cleaned_bis_3)
prmwindow <- moving_average(cleaned_prm)
```

Merge the moving_average output files into one larger data frame.  Pivot to create "nutrient" and "concentration" columns.
```{r}
complete <- bind_rows(bq1_window, bq2_window, bq3_window, prmwindow)
complete_and_longer <- complete |> 
  pivot_longer(
    cols = c(`NH4-N`, `NO3-N`, K, Ca, Mg),
    names_to = "nutrient", 
    values_to = "concentration"
    )
```


### Results
Plot the new data.
```{r}
ggplot(
  data = complete_and_longer,
  mapping = aes(
    x = window_start,
    y = concentration,
    linetype = Site
  )
) + geom_line()+
  facet_wrap(
    vars(nutrient), 
    scales = "free", 
    ncol = 1
  )
```

This graph shows nutrient concentrations over time in the four stream sites between 1986 and 1995.  The figure contains one plot for each nutrient (Ca, Mg, K, NH4-N, and NO3-N).  Line types denote different sites.